Bioverse: Origins of Life

### 2024-06-21 src/tex/ms.tex
describe fractions of EEC/inhabited planets in the different samples

\begin{figure}
    \script{inhabited_FGKM.py}
    \begin{centering}
        \includegraphics[width=\hsize]{figures/inhabited_FGKM}
        \caption{Host stars of all transiting planets, \glspl{EEC}, and inhabited planets. In a sample of \var{N_nautilus} transiting planets, most \glspl{EEC} and all inhabited planets orbit M~dwarfs.}
        \label{fig:inhabited_FGKM}
    \end{centering}
\end{figure}

As shown in Figure~\ref{fig:inhabited_FGKM}, the majority of \glspl{EEC} and all inhabited planets orbit M~dwarfs.

>>>>

\begin{figure}
    \script{inhabited_FGKM.py}
    \begin{centering}
        \includegraphics[width=\hsize]{figures/inhabited_FGKM}
        \caption{Host stars of all transiting \glspl{EEC} and inhabited planets.
        In the FGK sample, most \glspl{EEC} and all inhabited planets orbit K~dwarfs.
        In an M~dwarf sample of the same size, the fraction of inhabited planets is larger.
        }
        \label{fig:inhabited_FGKM}
    \end{centering}
\end{figure}

As shown in Figure~\ref{fig:inhabited_FGKM}, the majority of \glspl{EEC} orbit lower-mass stars.
The fraction of inhabited planets is highest in the M~dwarf sample due to the higher \gls{NUV} fluxes in the \gls{HZ} of these stars.
